\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-02-05 paper/ms.tex

Cotrending basis vectors (CBVs) correction consists in removing global correlated
systematics that occurs in a given channel [add reference]. The procedure of
designing the CBVs is discussed in [add reference].

Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs. The mathematical
structure of the cost function is a direct consequence of the statistical
assumptions made for data.

@@

Then, the cbv-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
(Tabby's star) can be written as follows
\begin{verbatim}
>>> from lightkurve.lightcurve import KeplerCBVCorrector
>>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
    ...                          "0084/008462852/kplr008462852-2011073133259_llc.fits")
>>> cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}
Fig~\ref{fig:cbv-correction} illustrates the correction.

@@

@@

As an example, Fig.~\ref{fig:cbv-correction-k2} illustrates the result after
estimating the first nine coefficients for CBV correciton on target
\texttt{EPIC 201543306}.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

\subsubsection{Number of CBVs}
The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}), which shows the cost
function as a function of the number of CBVs. Usually, as the number of
CBVs increases, the value of the cost function decreases. And therefore,
the user should empirically choose a number of CBVs which does not
remove the astrophysical signal of interest [add reference].
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

>>>>

Cotrending basis vectors (CBVs) can remove global correlated
systematics present in a given channel \cite{2012PASP..124.1000S}.

Given a set of $n$ CBVs, one is interested in finding a vector of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs. The mathematical
structure of the cost function is a direct consequence of the statistical
assumptions made for data.

@@

Then, the CBV-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

An example of SAP flux correction for target \texttt{KOI 8462852}
(Tabby's star) can be written as follows
\begin{verbatim}
>>> from lightkurve.lightcurve import KeplerCBVCorrector
>>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
    ...                          "0084/008462852/kplr008462852-2011073133259_llc.fits")
>>> cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

Fig~\ref{fig:cbv-correction} illustrates the correction.

@@

\cite{2014sdmm.book.....I}.

Improperly tuning the number of CBVs can cause over-/under-fitting. One
way to identify a reasonable number of CBVs is to perform a grid search
as shown in Fig~(\ref{fig:cbv-grid-search}).

@@

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{2014sdmm.book.....I}.

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

\subsubsection{Number of CBVs}
The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}), which shows the cost
function as a function of the number of CBVs. Usually, as the number of
CBVs increases, the value of the cost function decreases. And therefore,
the user should empirically choose a number of CBVs which does not
remove the astrophysical signal of interest [add reference].

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
% Do you use AIC or BIC or cross-validation?
An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.
